ML comparison

### 2020-10-11 src/s_ml.Rmd
runs of ml comparison done

f_replicate_gridded <- function(x, method_, caretGrids_){
  r_stars <- vector(length = nrow(caretGrids_))
  for(i in 1:nrow(caretGrids_))
    r_stars[i] <- r_star_ml_variety(x, method_, caretGrids_[i, ])
  return(r_stars)
}

f_run_all <- function(methods, list_of_caret_grids, f_data_generator){
  x <- f_data_generator()
  r_stars <- vector(length = length(methods))
  for(i in seq_along(r_stars))
    r_stars[i] <- max(f_replicate_gridded(x, methods[i], list_of_caret_grids[[i]]))
  return(tibble(r_star=r_stars, method=methods))
}

@@

tunegrid_gbm <- expand.grid(interaction.depth=3, 
                             n.trees = 50,
                             shrinkage=0.1,
                             n.minobsinnode=10)
tunegrid_rf <- tibble(mtry = 1:2)
tunegrid_knn <- tibble(k = c(5, 10, 15, 20, 40))
tunegrid_svm <- tibble(C = c(0.25, 0.5, 0.75))
tunegrid_multinom <- tibble(decay=c(0.1, 0.2, 0.5, 1))
```

@@

temp_df <- f_run_all_replicates(2, c("gbm", "rf", "knn", "svmLinear", "multinom"),
          list(tunegrid_gbm, tunegrid_rf, tunegrid_knn, tunegrid_svm, tunegrid_multinom),
          f_data_ar1)
```

@@

temp_df <- f_run_all_replicates(2, c("gbm", "rf", "knn", "svmLinear", "multinom"),
          list(tunegrid_gbm, tunegrid_rf, tunegrid_knn, tunegrid_svm, tunegrid_multinom),
          f_data_8_schools)
```

@@

temp_df <- f_run_all_replicates(2, c("gbm", "rf", "knn", "svmLinear", "multinom"),
          list(tunegrid_gbm, tunegrid_rf, tunegrid_knn, tunegrid_svm, tunegrid_multinom),
          f_data_cauchy)
```

# Multivariate normal
```{r}

```

>>>>

f_replicate_gridded <- function(x, method_, caretGrids_){
  r_stars <- vector(length = nrow(caretGrids_))
  times <- vector(length = nrow(caretGrids_))
  for(i in 1:nrow(caretGrids_)){
    start.time <- Sys.time()
    r_stars[i] <- r_star_ml_variety(x, method_, caretGrids_[i, ])
    end.time <- Sys.time()
    times[i] <- end.time - start.time
  }
  return(list(r_star=r_stars, time=times))
}

f_run_all <- function(methods, list_of_caret_grids, f_data_generator){
  x <- f_data_generator()
  r_stars <- vector(length = length(methods))
  times <- vector(length = length(methods))
  hypers <- vector(length = length(methods), mode="list")
  for(i in seq_along(r_stars)){
    print(methods[i])
    a_grid <- list_of_caret_grids[[i]]
    a <- f_replicate_gridded(x, methods[i], a_grid)
    r_stars[i] <- max(a$r_star)
    a_ind <- which.max(a$r_star)
    times[i] <- a$time[a_ind]
    hypers[[i]] <- a_grid[a_ind, ]
  }
  return(tibble(r_star=r_stars, method=methods, time=times, hyper=hypers))
}

@@

tunegrid_gbm <- expand.grid(interaction.depth=1, 
                             n.trees = c(400),
                             shrinkage=c(0.1),
                             n.minobsinnode=c(1))
tunegrid_rf <- tibble(mtry = c(1, 5, 15))
tunegrid_knn <- tibble(k = c(5, 10, 15, 20, 40))
tunegrid_svm <- tibble(C = c(0.25, 0.5, 0.75))
tunegrid_multinom <- tibble(decay=c(0.1, 0.2, 0.5, 1))
tunegrid_xgbtree <- expand_grid(nrounds = c(1, 10),
                       max_depth = c(1, 4),
                       eta = c(.1, .4),
                       gamma = 0,
                       colsample_bytree = .7,
                       min_child_weight = 1,
                       subsample = c(.8, 1))
```

@@

temp_df <- f_run_all_replicates(2, c("gbm", "rf", "knn", "svmLinear", "multinom"),
          list(tunegrid_gbm, tunegrid_rf, tunegrid_knn, tunegrid_svm, tunegrid_multinom),
          f_data_ar1)
temp_df <- readRDS("../data/ml_comp_hypers_set_ar1.rds")
temp_df %>%
  ggplot(aes(x=as.factor(method), y=r_star)) +
  geom_boxplot()
```

@@

temp_df <- f_run_all_replicates(2, c("gbm", "rf", "knn", "svmLinear", "multinom"),
          list(tunegrid_gbm, tunegrid_rf, tunegrid_knn, tunegrid_svm, tunegrid_multinom),
          f_data_8_schools)

temp_df <- readRDS("../data/ml_comp_hypers_set_8_schools.rds")
temp_df %>%
  ggplot(aes(x=as.factor(method), y=r_star)) +
  geom_boxplot()
temp_df %>%
  ggplot(aes(x=time, y=r_star, colour=as.factor(method))) +
  geom_jitter()
```

@@

temp_df <- f_run_all_replicates(2, c("gbm", "rf", "knn", "svmLinear", "multinom"),
          list(tunegrid_gbm, tunegrid_rf, tunegrid_knn, tunegrid_svm, tunegrid_multinom),
          f_data_cauchy)
temp_df <- readRDS("../data/ml_comp_hypers_set_cauchy.rds")
temp_df %>%
  ggplot(aes(x=as.factor(method), y=r_star)) +
  geom_boxplot()
temp_df %>%
  ggplot(aes(x=time, y=r_star, colour=as.factor(method))) +
  geom_jitter()
```

# Multivariate normal
```{r}
f_data_normal <- function(){
  N <- 250
  A <- rWishart(1, 250, diag(N))[,,1]
  model <- stan_model("mvt_250_ncp.stan")
  fit <- sampling(model, data=list(N=N, A=A), iter=1000, chains=4)
  x <- rstan::extract(fit, permuted=F)
  return(x)
}

temp_df <- f_replicate_gridded(x, "rf", tunegrid_rf)

temp_df <- readRDS("../data/ml_comp_hypers_set_normal_250.rds")
temp_df %>%
  ggplot(aes(x=as.factor(method), y=r_star)) +
  geom_boxplot()
temp_df %>%
  ggplot(aes(x=as.factor(method), y=time)) +
  geom_boxplot()

temp_df %>%
  ggplot(aes(x=time, y=r_star, colour=as.factor(method))) +
  geom_jitter()
```

# Check for false positives with random forests
```{r}
f_data_converged <- function(){
  d <- 10
  n <- 2000
  nchain <- 4

  x <- rnorm(d * n * nchain)
  x <- array(x, dim=c(n, nchain, d))
  return(x)
}

temp_df <- f_run_all_replicates(10, c("gbm", "rf"),
          list(tunegrid_gbm, tunegrid_rf),
          f_data_converged)
temp_df %>% 
  ggplot(aes(x=as.factor(method), y=r_star)) +
  geom_boxplot()
```

# Setting hyperparameters for random forest:
"Influence of Hyperparameters on Random Forest Accuracy"
Simon Bernard, Laurent Heutte, Sebastien Adam, 2009
Use mtry=sqrt(number features)

whereas for gbms / xgboost, performance depends on lots of things
